Ecological Metadata Language interface for R: facilitating synthesis and integration of heterogenous data

### 2014-04-22 inst/doc/pubs/manuscript.Rmd
update affiliations

---
layout: preprint
#layout: review, 11pt
title: "Ecological Metadata Language interface for R: facilitating synthesis and integration of heterogenous data"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig@gmail.com
    footnote: Corresponding author
  - name: Karthik Ram 
    affiliation: Berkeley 
  - name: Class-Thido Pfaff
    affiliation: Leipzig
  - name: Matt Jones 
    affiliation: NCEAS 
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA

>>>>

---
layout: preprint
#layout: review, 11pt
title: "Ecological Metadata Language interface for R: facilitating synthesis and integration of heterogenous data"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig@gmail.com
    footnote: Corresponding author
  - name: Karthik Ram 
    affiliation: Berkeley 
  - name: Class-Thido Pfaff
    affiliation: Leipzig
  - name: Matt Jones 
    affiliation: NCEAS 
address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research, 
      Department of Applied Math and Statistics, 
      University of California, Mail Stop SOE-2,
      Santa Cruz, CA 95064, USA
  - code: Berkeley
    address: |
      Department of Environmental Science and Policy Management,
      University of California, Berkeley, 130 Mulford Hall,
      Berkeley, CA 94720. USA
  - code: Leipzig
    address: 
  - code: NCEAS
    address |
      National Center for Ecological Analysis and Synthesis,
      735 State Street, Suite 300, 
      Santa Barbara, CA 93101
